Title here

### 2025-04-17 proposal.tex
abstract draft ks

\abstract{Enter the text of your abstract here.}

\begin{document}

>>>>

\abstract{As of 2022, nearly 5 million smallholder farmers across a dozen countries are covered by Anticipatory Action (AA) programs \citep{chaves-gonzalez_anticipatory_2022}, which are aid schemes triggered if seasonal forecasts of rainfall cross a locally-determined threshold. By compensating farmers when yields are expected to be low, AA programs can help smooth risks, enhance food security, and reduce the likelihood of disaster-induced displacement \citep{thalheimer_forecast-based_2020,XX}. AA thresholds are often calculated to meet a donor or government [XX] trigger frequency; for example, [XX]’s AA program intends to trigger in the worst 20\% [XX] of seasons by expected agricultural yield. However, the observational rainfall record in many regions with AA programs is limited, and interannual or even interdecadal autocorrelation in the climate patterns that affect seasonal rainfall further reduces the effective sample size used to calculate these thresholds. This suggests that AA triggers may be highly sensitive to the available sample size of the observational record, increasing the risk that, due to poorly specified thresholds, either action is not triggered when it is needed or programs become financially unsustainable. In practice, forecasters are aware of this uncertainty, and ad hoc decisions on whether to trigger action are often made if seasonal forecasts are close to the threshold. To better support decision-making and formalize a process of determining whether a threshold for action may be crossed, we develop locally-defined confidence intervals for AA thresholds by recalculating triggers using bootstrap resampling of the observational record. We find that, though [XX], in regions with [XX characteristics/teleconnections/etc.], AA triggers are particularly unstable, [XX raising questions about the suitability of simple thresholds there] [XX alternatively; we find confidence intervals are narrow in most places, supporting the use of simple triggers...]

[XX something something, these triggers are likely to be nonstationary in a changing climate as well. I think \citep{coughlan_de_perez_adapting_2022} says something about that]}
\begin{document}
